Harmony: A Verifiable Systems Programming Language

### 2022-01-15 paper/paper.tex

<{:const:tas}>
<{:const:cas}>
<{:const:BinSem}>
<{:const:Semaphore}>
<{:const:__init__}>
<{:const:p}>
<{:const:hello}>
<{:const:enqueue}>
<{:const:dequeue}>
<{:const:send}>
<{:const:receive}>

@@

def thread(self):
    if choose({ "deq", "enq" }) == "enq":
        print("call enqueue", self)
        queue.enqueue(?q, self)
        print("done enqueue", self)
    else:
        print("call dequeue", self)
        let v = queue.dequeue(?q):
            print("done dequeue", self, v)

for i in {1..NOPS}: spawn thread(i)
<{:end:}>
\end{tcolorbox}
}
\\
(a) concurrent <{queue}> module & (b) test program
\end{tabular}
\end{center}
\caption{The (a) specification and (b) test program for a concurrent queue}
\label{fig:queue}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\begin{tabular}{l|c|c|c|c}
           & <{NOPS=1}> & <{NOPS=2}> & <{NOPS=3}> & <{NOPS=4}> \\ \hline\hline
queue specification    & 11/0.3 & 110/0.3 &  1,286/0.4 &  16,332/0.9 \\ \hline
queue impl. w/o check  & 20/0.5 & 383/0.6 &  8,874/0.8 & 261,878/12.7 \\ \hline
queue impl. with check & 20/0.5 & 425/0.6 & 10,977/1.0 & 437,226/23.6 \\
\end{tabular}
\end{center}
\caption{The number of states generated by the model checker and the
execution time (in seconds) for running \autoref{fig:queue}(b).
This is done for three configurations, varying the value of <{NOPS}>:
the specification (\autoref{fig:queue}(a)), a simple linked list
implementation using locks, and the same implementation combined with
the behavior automaton generated by the first configuration.}
\label{fig:qcmp}
\end{figure*}

>>>>

<{:const:tas}>
<{:const:cas}>
<{:const:BinSem}>
<{:const:Semaphore}>
<{:const:__init__}>
<{:const:p}>
<{:const:hello}>
<{:const:enqueue}>
<{:const:dequeue}>
<{:const:enq_test}>
<{:const:deq_test}>
<{:const:send}>
<{:const:receive}>

@@

def enq_test(self):
    print("call enqueue", self)
    queue.enqueue(?q, self)
    print("done enqueue", self)

def deq_test(self):
    print("call dequeue", self)
    let v = queue.dequeue(?q):
        print("done dequeue", self, v)

nenq = choose {1..NOPS-1}
for i in {1..nenq}:      spawn enq_test(i)
for i in {1..NOPS-nenq}: spawn deq_test(i)
<{:end:}>
\end{tcolorbox}
}
\\
(a) concurrent <{queue}> module & (b) test program
\end{tabular}
\end{center}
\caption{The (a) specification and (b) test program for a concurrent queue}
\label{fig:queue}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\begin{tabular}{l|c|c|c|c}
           & <{NOPS=2}> & <{NOPS=3}> & <{NOPS=4}> & <{NOPS=5}> \\ \hline\hline
queue specification    &  30/0.0 &  350/0.0 &  3,385/0.0 &    32,010/0.1 \\ \hline
queue impl. w/o check  &  90/0.0 & 1905/0.0 & 39,519/0.1 & 1,089,222/5.6 \\ \hline
queue impl. with check & 101/0.0 & 2566/0.0 & 75,974/0.3 & 3,400,555/22.8 \\
\end{tabular}
\end{center}
\caption{The number of states generated by the model checker and the
execution time (in seconds) for running \autoref{fig:queue}(b).
This is done for three configurations, varying the value of <{NOPS}>:
the specification (\autoref{fig:queue}(a)), a simple linked list
implementation using locks, and the same implementation combined with
the behavior automaton generated by the first configuration.  The
hardware consisted of a 2.8 GHz Quad-Core Intel Core i7
(2 hyperthreads per core) with 2,133 MHz LPDDR3 memory.}
\label{fig:qcmp}
\end{figure*}
